---
title: "rOpenSci submission templates for bdverse"
author: "Sunny Dhoke, Tomer Gueta"
date: "26/07/2020"
output:
  rmarkdown::html_document:
    theme: lumen
    highlight: espresso 
    toc: true
    toc_float: true
    toc_collapsed: false
toc_depth: 3
number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

Create a copy of this template for your R package and fill out details as necessary. This template should be a good starting point for any package planning fot rOpenSci submission.

## Checklist

You need to make sure following things are done before package is ready for submission.
Make sure README is upto rOpenSci standards. Checkout [this cool README example](https://github.com/ropensci/drake) or [this](https://github.com/ropensci/ijtiff#ijtiff-) one. Second one's README is short and sweet.

### README file of your package 

README.md should have below things mentioned to make user understand what your R package is about.

Template:

```
#### Package Name

#### Badges

Preferably in a wide table format. [See this cool README example](https://github.com/ropensci/drake) 

- [ ] CI. Should be working and available on all major OS versions. R versions can be 
- [ ] test coverage. We need Maturing.
- [ ] lifecycle badge. We need Active instead of WIP badge. 
- [ ] repostatus.org badge. You can run `rodev::use_repostatus_badge()` to add badge.
- [ ] badge for rOpenSci peer-review once it has started.

#### Short Description

- [ ] Goal of package:
- [ ] Descriptive links to all vignettes(rendered):

#### Installation Instructions

#### Any extra setup steps required?If yes, mention them.

#### Brief Demonstration Usage of package

#### Any similar package(s) exist? If yes, how it relates to other packages?

#### Citation Information

---

### Pre-Submission rOpenSci checklist template

#### Which category or categories this package should fall under.

Refer official [package fit policy](https://ropensci.github.io/dev_guide/policies.html#package-categories)
Please read the policy carefully before marking below categories.

- [ ] Data retrieval
- [ ] Data Extraction
- [ ] Data munging
- [ ] Data deposition
- [ ] Data validation and testing
- [ ] Workflow automation
- [ ] Version Control
- [ ] Citation management an bibliometrics
- [ ] Scientific software wrappers
- [ ] Field and laboratory reproducibility tools
- [ ] Database software bindings
- [ ] Geospatial data
- [ ] Text analysis

#### How and Why these categories?

Just brief,1-2 lines description will suffice.

#### Target audience and Scientific applications

Who is target audience and what are scientific applications of this package?

#### Any other similar R packages?

If yes,how your R package is better than what rOpenSci already has?

#### Other questions and Issues rOpenSci should know?


```
---

### rOpenSci official Package Review template for Reviewers


```

## Package Review

*Please check off boxes as applicable, and elaborate in comments below.  Your review is not limited to these topics, as described in the reviewer guide*

- **Briefly describe any working relationship you have (had) with the package authors.**
- [ ] As the reviewer I confirm that there are no [conflicts of interest](https://devguide.ropensci.org/policies.html#coi) for me to review this work (If you are unsure whether you are in conflict, please speak to your editor _before_ starting your review).

#### Documentation

The package includes all the following forms of documentation:

- [ ] **A statement of need** clearly stating problems the software is designed to solve and its target audience in README
- [ ] **Installation instructions:** for the development version of package and any non-standard dependencies in README
- [ ] **Vignette(s)** demonstrating major functionality that runs successfully locally
- [ ] **Function Documentation:** for all exported functions in R help
- [ ] **Examples** for all exported functions in R Help that run successfully locally
- [ ] **Community guidelines** including contribution guidelines in the README or CONTRIBUTING, and DESCRIPTION with `URL`, `BugReports` and `Maintainer` (which may be autogenerated via `Authors@R`).

>##### For packages co-submitting to JOSS
>
>- [ ] The package has an **obvious research application** according to [JOSS's definition](https://joss.theoj.org/about#submission_requirements)
>
>The package contains a `paper.md` matching [JOSS's requirements](https://joss.theoj.org/about#paper_structure) with:
>
>- [ ] **A short summary** describing the high-level functionality of the software
>- [ ] **Authors:**  A list of authors with their affiliations
>- [ ] **A statement of need** clearly stating problems the software is designed to solve and its target audience.
>- [ ] **References:** with DOIs for all those that have one (e.g. papers, datasets, software).

#### Functionality

- [ ] **Installation:** Installation succeeds as documented.
- [ ] **Functionality:** Any functional claims of the software been confirmed.
- [ ] **Performance:** Any performance claims of the software been confirmed.
- [ ] **Automated tests:** Unit tests cover essential functions of the package
   and a reasonable range of inputs and conditions. All tests pass on the local machine.
- [ ] **Packaging guidelines**: The package conforms to the rOpenSci packaging guidelines

#### Final approval (post-review)

- [ ] **The author has responded to my review and made changes to my satisfaction. I recommend approving this package.**

Estimated hours spent reviewing:

- [ ] Should the author(s) deem it appropriate, I agree to be acknowledged as a package reviewer ("rev" role) in the package DESCRIPTION file.


### Review Comments

```

---

### Commands for checks done by rOpenSci reviewer.

#### Install package

```{r}
devtools::install(dependencies = TRUE)
```

#### Does it pass RCMD check?

```{r}
devtools::check() 
```

```{r}
devtools::test()
```

#### Test coverage 75% above?

```{r}
install.packages("covr")

covr::package_coverage()
```
If not,additional tests and explanation needed before sent for review.

#### CI 

Use code coverage report to identify untested lines and add further tests.
[Official rOpenSci CI doc](https://devguide.ropensci.org/ci.html#coverage)

#### Following good practices?

Run following command to find errors and style issues. 
You can justify why such style for package,if following any particular one.

```{r}
install.packages("goodpractice")
goodpractice::gp()
```
### Spelling 



```{r}
devtools::spell_check()
```
For package 
```{r}
#refer  https://github.com/ropensci/spelling

spelling::spell_check_package()
```
and for README.Rmd

```{r}
spelling::spell_check_files("README.Rmd")
```

If you have done all of the above steps,the package is ready for official submission as per rOpenSci guidelines.
Make sure all README are ready with Examples. Checkout [this cool README example](https://github.com/ropensci/drake) or [this](https://github.com/ropensci/ijtiff#ijtiff-) one. Second one's README is short and sweet.
